\boldmath Heavy resonances at energy frontier colliders

### 2019-02-04 paper.tex
Updates from ShareLaTeX

\end{tabular}
\caption{Tracking-related parameters for the HELHC and FCC detectors in Delphes.}
\label{tab:trk_param}
\end{center}
\end{table}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$\sigma(E)/E $ (ECAL)& 10\%/$\sqrt{E} \oplus 1\%$ &  10\%/$\sqrt{E} \oplus 1\%$\\
   \hline
$\sigma(E)/E $ (HCAL)& 50\%/$\sqrt{E} \oplus 3\%$  &  50\%/$\sqrt{E} \oplus 3\%$\\
  \hline
  \hline
$\eta \times \phi$ cell size (ECAL)& $(0.02\times0.02)$ &  $(0.01\times0.01)$\\
  \hline
 $\eta \times \phi$ cell size  (HCAL)& $(0.1\times0.1)$ & $(0.025\times0.025)$
\end{tabular}
\caption{Calorimeter parameters for the HELHC and FCC detectors in Delphes.}
\label{tab:cal_param}
\end{center}
\end{table}
%\caption{Comparison of basic detector performances for FCC-hh and HE-LHC.}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HE-LHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC-hh & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HELHC and FCC detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

@@

\begin{table}[htb!]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
  $4-8$ & > 2.4 & > 2.5 and < 3.5 & > 400 GeV\\
  $10$ & > 2.4 & > 2.7 and < 4 & > 300 GeV\\
  $12-14$ & > 2.6 & > 2.7 and < 4 & > 300 GeV\\
  $16-18$ & > 2.7 & > 2.7 and < 4 & > 300 GeV\\
  $>18$ & > 2.8 & > 3 and < 4 & > 300 GeV\\
  \hline
  \end{tabular}
  \caption{List of mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ search.}
  \label{tab:leptonicresonances:tautau}
\end{table}

@@

\begin{table}[!htb]
   \centering
\begin{tabular}{|l|l|c|r|}
  \hline
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
   $2$ & > 2.4 & > 2.4 and < 3.9 & > 80 GeV\\
   $4$ & > 2.4 & > 2.7 and < 4.4 & > 80 GeV\\
   $6$ & > 2.4 & > 2.9 and < 4.4 & > 80 GeV\\
   $8$ & > 2.6 & > 2.9 and < 4.6 & > 80 GeV\\
  $10$ & > 2.8 & > 2.9 and < 4.1 & > 60 GeV\\
%  $12$ & > 2.8 & > 3.0 and < 3.6 & > 60 GeV\\
%  $14$ & > 3.0 & > 3.0 and < 3.3 & > 60 GeV\\
  \hline
  \end{tabular}
  \caption{Mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ resonance search.}
  \label{tab:leptonicresonances:tautau27}
\end{table}

@@

%
\begin{table}
\centering
\begin{tabular}{|l|c|c|c|} \hline\hline
  Model &   95$\%$ \cl  &  $3\sigma$  & $5\sigma$   \\
\hline
SSM    &     6.62     &  6.09    &  5.62     \\
LRM    &   6.39     & 5.85     & 5.39  \\
$\psi$    &  6.10   & 5.55   & 5.07  \\
$\chi$   &  6.22    & 5.68    & 5.26   \\
$\eta$   &  6.15     &  5.59  &  5.16   \\
~I        & 5.98   &  5.45   &  5.05  \\
\hline\hline
\end{tabular}
\caption{ Mass reach for several $Z'$ models at \sqrtslhc\ with \intlumihllhc. }
\label{tab:pheno:spec}
\end{table}
%

>>>>

\end{tabular}
\caption{Tracking-related parameters for the HE-LHC and FCC-hh detectors in Delphes.}
\label{tab:trk_param}
\end{center}
\end{table}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{l||c|c}
& HE-LHC & FCC-hh \\
  \hline
  \hline
$\sigma(E)/E $ (ECAL)& 10\%/$\sqrt{E} \oplus 1\%$ &  10\%/$\sqrt{E} \oplus 1\%$\\
   \hline
$\sigma(E)/E $ (HCAL)& 50\%/$\sqrt{E} \oplus 3\%$  &  50\%/$\sqrt{E} \oplus 3\%$\\
  \hline
  \hline
$\eta \times \phi$ cell size (ECAL)& $(0.02\times0.02)$ &  $(0.01\times0.01)$\\
  \hline
 $\eta \times \phi$ cell size  (HCAL)& $(0.1\times0.1)$ & $(0.025\times0.025)$
\end{tabular}
\caption{Calorimeter parameters for the HE-LHC and FCC-hh detectors in Delphes.}
\label{tab:cal_param}
\end{center}
\end{table}
%\caption{Comparison of basic detector performances for FCC-hh and HE-LHC.}

@@

\begin {table}[htb!]
\begin{center}
\begin{tabular}{ l | c | c | c | c | c }
  & electrons & muons & photons & b-jets & $\tau$-jets\\
  \hline
  \hline
HE-LHC & 95\% & 95\% & 95\% & (1 - \pt~[TeV]/5)$\cdot$75\% & (1 - \pt~[TeV]/5)$\cdot$60\%  \\
FCC-hh & 99\% & 95\% & 95\%  & (1 - \pt~[TeV]/15)$\cdot$85\% & (1 - \pt~[TeV]/30)$\cdot$60\% \\
\end{tabular}
\caption{Global reconstruction efficiency of high \pt\ central objects for the HE-LHC and FCC-hh detectors in Delphes.}
\label{tab:effs}
\end{center}
\end{table}

@@

\begin{table}[htb!]
   \centering
\begin{tabular}{c|c|c|c}
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
  \hline
  $4-8$ & > 2.4 & > 2.5 and < 3.5 & > 400 GeV\\
  $10$ & > 2.4 & > 2.7 and < 4 & > 300 GeV\\
  $12-14$ & > 2.6 & > 2.7 and < 4 & > 300 GeV\\
  $16-18$ & > 2.7 & > 2.7 and < 4 & > 300 GeV\\
  $>18$ & > 2.8 & > 3 and < 4 & > 300 GeV\\
  \end{tabular}
  \caption{List of mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ search.}
  \label{tab:leptonicresonances:tautau}
\end{table}

@@

\begin{table}[!htb]
   \centering
\begin{tabular}{c|c|c|c}
   $\Zp$ mass [TeV] &  $\Delta \phi(\tau_1, \tau_2)$&  $\Delta R(\tau_1, \tau_2)$ & $\met$\\
  \hline
  \hline
   $2$ & > 2.4 & > 2.4 and < 3.9 & > 80 GeV\\
   $4$ & > 2.4 & > 2.7 and < 4.4 & > 80 GeV\\
   $6$ & > 2.4 & > 2.9 and < 4.4 & > 80 GeV\\
   $8$ & > 2.6 & > 2.9 and < 4.6 & > 80 GeV\\
  $10$ & > 2.8 & > 2.9 and < 4.1 & > 60 GeV\\
%  $12$ & > 2.8 & > 3.0 and < 3.6 & > 60 GeV\\
%  $14$ & > 3.0 & > 3.0 and < 3.3 & > 60 GeV\\
  \end{tabular}
  \caption{Mass dependent cuts optimised to maximise the sensitivity for the \Zptata\ resonance search.}
  \label{tab:leptonicresonances:tautau27}
\end{table}

@@

%
\begin{table}
\centering
\begin{tabular}{c|c|c|c}

  Model &   95$\%$ \cl  &  $3\sigma$  & $5\sigma$   \\
\hline
\hline
SSM    &     6.62     &  6.09    &  5.62     \\
LRM    &   6.39     & 5.85     & 5.39  \\
$\psi$    &  6.10   & 5.55   & 5.07  \\
$\chi$   &  6.22    & 5.68    & 5.26   \\
$\eta$   &  6.15     &  5.59  &  5.16   \\
~I        & 5.98   &  5.45   &  5.05  \\
\end{tabular}
\caption{ Mass reach for several $Z'$ models at \sqrtslhc\ with \intlumihllhc. }
\label{tab:pheno:spec}
\end{table}
%
